### 2018-08-18 doc/paper.tex
Finishing paper.

\usepackage{amsthm,amssymb,amsmath}
\usepackage{bm}
%% H/T: https://tex.stackexchange.com/a/28334/32270
\usepackage{chngcntr}
\counterwithin{equation}{section}
%% H/T: https://tex.stackexchange.com/a/71153/32270
\usepackage[nottoc,notlot,notlof]{tocbibind}

@@

\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{A Curious Case of Curbed Condition}
\rhead{Danny Hermes}

@@

\begin{abstract}
\noindent We present a short note describing a condition number
of the intersection of two B\'{e}zier curves. Since tangent
intersections are to transversal intersections as multiple roots are
to simple roots of a function, this condition number is infinite
for non-transveral intersections.
\\ \\
\noindent \textit{Keywords}: B\'{e}zier curve, Curve intersection,
Condition number
\end{abstract}

@@

Placeholder

\section{Problem conditioning}\label{sec:conditioning}

Consider a smooth function \(F: \reals^n \longrightarrow \reals^n\)
with Jacobian \(F_{\bm{x}} = J\). We want to consider a special class of
functions of the form \(F\left(\bm{x}\right) = \sum_j c_j
\phi_j\left(\bm{x}\right)\) where the basis
functions \(\phi_j\) are also smooth functions on \(\reals^n\)
and each \(c_j \in \reals\). We want to consider the effects on a root
\(\bm{\alpha} \in \reals^n\) of a perturbation in one of the
coefficients \(c_j\). We examine the perturbed functions
\begin{equation}
G(x, \delta) = F\left(\bm{x}\right) + \delta \phi_j\left(\bm{x}\right).
\end{equation}
Since \(G\left(\bm{\alpha}, 0\right) = \bm{0}\), if \(J^{-1}\) exists at
\(\bm{x} = \bm{\alpha}\) then
the implicit function theorem tells us that we can define
\(\bm{x}\) via
\begin{equation}
G\left(\bm{x}\left(\delta\right), \delta\right) = \bm{0}.
\end{equation}
Taking the derivative with respect to \(\delta\) we find that
\(\bm{0} = G_{\bm{x}} \bm{x}_{\delta} + G_{\delta}\). Plugging in
\(\delta = 0\) we find that \(0 = J\left(\bm{\alpha}\right) \bm{x}_{\delta} +
\phi_j\left(\bm{\alpha}\right)\), hence we
conclude that
\begin{equation}
\bm{x}\left(\delta\right) = \bm{\alpha} - J\left(\bm{\alpha}\right)^{-1}
  \phi_j\left(\bm{\alpha}\right) \delta + \bigO{\delta^2}.
\end{equation}
This gives a relative condition number (for the root) of
\begin{equation}
\frac{\left \lVert J\left(\bm{\alpha}\right)^{-1}
  \phi_j\left(\bm{\alpha}\right) \right \rVert}{
  \left \lVert \bm{\alpha} \right \rVert}.
\end{equation}

By considering perturbations in \emph{all} of the coefficients:
\(\left|\delta_j\right| \leq \eps \left|c_j\right|\), a similar analysis
gives a root function
\begin{equation}
\bm{x}\left(\delta_0, \ldots, \delta_n\right) = \bm{\alpha} -
  J\left(\bm{\alpha}\right)^{-1} \sum_{j = 0}^n \delta_j
  \phi_j\left(\bm{\alpha}\right) + \bigO{\eps^2}.
\end{equation}
With this, we can define a root condition number
\begin{equation}\label{eq:abstract-cond-num}
\kappa_{\bm{\alpha}} =
  \lim_{\eps \to 0} \left(\sup \frac{\left \lVert\delta \bm{\alpha}
  \right \rVert / \eps}{\left \lVert\bm{\alpha}\right \rVert}\right) =
  \lim_{\eps \to 0} \left(\sup \frac{\left \lVert
  J\left(\bm{\alpha}\right)^{-1} \sum_j \delta_j
  \phi_j\left(\bm{\alpha}\right) \right \rVert / \eps}{
  \left \lVert\bm{\alpha}\right \rVert}\right).
\end{equation}

When \(n = 1\), \(J^{-1}\) is simply \(1 / F'\) and we find
\begin{equation}
\kappa_{\alpha} =
  \frac{1}{\left|\alpha F'(\alpha)\right|} \sum_{j = 0}^n \left|
  c_j \phi_j(\alpha)\right|.
\end{equation}
This value is given by the triangle inequality applied to
\(\delta \alpha\)  and equality can be attained since the sign
of each \(\delta_j = \pm c_j \eps\) can be modified at will to make
\(\phi_j(\alpha) \delta_j = \left|\phi_j(\alpha) c_j\right| \eps\).

When \(n > 1\), the triangle inequality tells us that
\begin{equation}
\kappa_{\bm{\alpha}} =
  \lim_{\eps \to 0} \left(\sup \frac{\left \lVert\delta \bm{\alpha} /
  \eps\right \rVert}{\left \lVert\bm{\alpha}\right \rVert}\right) \leq
  \frac{1}{\left \lVert\bm{\alpha}\right \rVert} \sum_{j = 0}^n
  \left|c_j\right| \left \lVert J\left(\bm{\alpha}\right)^{-1}
  \phi_j(\bm{\alpha})\right \rVert.
\end{equation}
However, this bound is only attainable if all
\(\phi_j(\bm{\alpha})\) are parallel. However, we'll seldom need to
compute the exact condition number and are instead typically
interested in the order of magnitude. In this case a lower
bound
\begin{equation}
\frac{1}{\left \lVert\bm{\alpha}\right \rVert}
\max_j \left|c_j\right| \left \lVert J\left(\bm{\alpha}\right)^{-1}
\phi_j(\bm{\alpha})\right \rVert
\end{equation}
for \(\kappa_{\bm{\alpha}}\)
will suffice as an approximate condition number.

For an example, consider
\begin{equation}
\phi_0 = \left[ \begin{array}{c} x_0 \\ 2 \\ 0 \end{array}\right],
\phi_1 = \left[ \begin{array}{c} 0 \\ x_1 \\ 3 \end{array}\right],
\phi_2 = \left[ \begin{array}{c} 2 \\ 0 \\ x_2 \end{array}\right],
F = \phi_0 + 2 \phi_1 + 3 \phi_2,
\bm{\alpha} = \left[ \begin{array}{c} -6 \\ -1 \\ -2 \end{array}\right].
\end{equation}
For a given \(\eps\), the maximum root perturbation occurs when
\(\delta_0 = \eps, \delta_1 = 2 \eps, \delta_2 = -3 \eps\) and
gives
\(\left \lVert J\left(\bm{\alpha}\right)^{-1} \sum_j
\delta_j \phi_j\left(\bm{\alpha}\right) \right \rVert
= 4 \sqrt{10} \eps \approx 12.65 \eps\).
The pessimistic triangle inequality bound gives
\(\sum_j \left|c_j\right| \left \lVert J\left(\bm{\alpha}\right)^{-1}
\phi_j(\bm{\alpha})\right \rVert \approx 14.64 \eps\) and the
maximum individual perturbation is \(2 \sqrt{10} \eps \approx 6.325 \eps\)
(this occurs when \(\delta_0 = \delta_1 = 0, \delta_2 = \pm 3 \eps\)).

In this general framework, we can define a condition number both
for a simple root of a polynomial in Bernstein form and for the
intersection of two planar B\'{e}zier curves. For the first,
\(\phi_j(s) = \binom{n}{j} (1 - s)^{n - j} s^j\) the Bernstein basis
functions, a polynomial \(p(s) = \sum_j b_j \phi_j(s)\) with
a simple root \(\alpha \in \left(0, 1\right]\) has root condition number
\begin{equation}
\kappa_{\alpha} =
  \frac{1}{\alpha \left|p'(\alpha)\right|} \sum_{j = 0}^n \left|
  b_j \phi_j(\alpha)\right| = \frac{\widetilde{p}(\alpha)}{
  \alpha \left|p'(\alpha)\right|}.
\end{equation}
For the intersection of a degree \(m\) curve \(b_1(s)\) and
a degree \(n\) curve \(b_2(t)\), we have basis functions
\begin{multline}
\phi_{0, -1, 1} = \left[ \begin{array}{c} B_{0, m}(s) \\ 0 \end{array}\right],
\phi_{0, -1, 2} = \left[ \begin{array}{c} 0 \\ B_{0, m}(s) \end{array}\right],
\cdots, \\
\phi_{m, -1, 1} = \left[ \begin{array}{c} B_{m, m}(s) \\ 0 \end{array}\right],
\phi_{m, -1, 2} = \left[ \begin{array}{c} 0 \\
  B_{m, m}(s) \end{array}\right], \\
\phi_{-1, 0, 1} = \left[ \begin{array}{c} -B_{0, n}(t) \\
  0 \end{array}\right],
\phi_{-1, 0, 2} = \left[ \begin{array}{c} 0 \\
  -B_{0, n}(t) \end{array}\right], \cdots, \\
\phi_{-1, n, 1} = \left[ \begin{array}{c} -B_{n, n}(t) \\
  0 \end{array}\right], \phi_{-1, n, 2} = \left[ \begin{array}{c} 0 \\
  -B_{n, n}(t) \end{array}\right].
\end{multline}
Since \(F(s, t) = b_1(s) - b_2(t)\) we have Jacobian \(J(s, t) =
\left[ \begin{array}{c c} b_1'(s) & -b_2'(t) \end{array}\right]\). We'll
consider a transversal intersection \(F(\alpha, \beta) = \bm{0}\) with
\(\det J(\alpha, \beta) \neq 0\). Since each of the
\(\phi_j\) is just a scalar multiple of the standard basis
vectors, writing \(J^{-1} = \left[ \begin{array}{c c}
\bm{v}_1 & \bm{v}_2 \end{array}\right]\), we have
\begin{multline}
J\left(\alpha, \beta\right)^{-1} \sum_{\bm{j}} \delta_{\bm{j}}
  \phi_{\bm{j}}\left(\alpha, \beta\right) = \left[\sum_{i = 0}^m
  \delta_{i, -1, 1} B_{i, m}\left(\alpha\right) + \sum_{j = 0}^n
  \delta_{-1, j, 1} B_{j, n}\left(\beta\right)\right] \bm{v}_1 \\
+ \left[\sum_{i = 0}^m
  \delta_{i, -1, 2} B_{i, m}\left(\alpha\right) + \sum_{j = 0}^n
  \delta_{-1, j, 2} B_{j, n}\left(\beta\right)\right] \bm{v}_2 =
  \nu_1 \bm{v}_1 + \nu_2 \bm{v}_2.
\end{multline}
where
\begin{equation}\label{eq:nu-bounds}
\left|\nu_k\right| / \eps \leq \sum_{i = 0}^m
  \left|c_{i, -1, k}\right| B_{i, m}\left(\alpha\right) + \sum_{j = 0}^n
  \left|c_{-1, j, k}\right| B_{j, n}\left(\beta\right) = \mu_k
\end{equation}
and the bound can be attained for both \(k = 1, 2\) by making the
signs of the \(\delta_{\bm{j}}\) agree. If we name the components of each
curve via
\(b_1(s) = \left[ \begin{array}{c c} x_1(s) & y_1(s) \end{array}\right]^T\)
and \(b_2(t) = \left[ \begin{array}{c c} x_2(t) & y_2(t) \end{array}\right]^T\)
then we see that \(\mu_1 = \widetilde{x}_1(\alpha) + \widetilde{x}_2(\beta)\)
and \(\mu_2 = \widetilde{y}_1(\alpha) + \widetilde{y}_2(\beta)\).
Thus we have condition number
\begin{align}
\kappa_{\alpha, \beta} &= \frac{1}{\sqrt{\alpha^2 + \beta^2}}
  \max_{\left|\nu_k\right| \leq \mu_k} \left \lVert \nu_1 \bm{v}_1 +
  \nu_2 \bm{v}_2 \right \rVert_2 \\
  &=
  \sqrt{\frac{\max_{\left|\nu_k\right| \leq \mu_k}
  \nu_1^2 \left(\bm{v}_1 \cdot \bm{v}_1\right) +
  2 \nu_1 \nu_2 \left(\bm{v}_1 \cdot \bm{v}_2\right) +
  \nu_2^2 \left(\bm{v}_2 \cdot \bm{v}_2\right)}{\alpha^2 + \beta^2}}
  \label{eq:intersect-cond-num}.
\end{align}
Since \(J^{-1}\) is invertible, we know \(\bm{v}_1\) and \(\bm{v}_2\) are
not parallel which can be used to show that the only internal critical
point of the function to be maximimized in~\eqref{eq:intersect-cond-num}
is \(\nu_1 = \nu_2 = 0\), which is the global minimum. Along the boundary of
the rectangle
\(\left[-\mu_1, \mu_1\right] \times \left[-\mu_2, \mu_2\right]\),
we fix one of \(\nu_1\) or \(\nu_2\) and the resulting univariate function is
an up-opening parabola, hence any critical point must be a local
minimum. Thus we know the maximum occurs at two of the four corners of the
rectangle:
\begin{equation}\label{eq:intersect-cond-num-too}
\kappa_{\alpha, \beta} = \sqrt{\frac{\mu_1^2
  \left(\bm{v}_1 \cdot \bm{v}_1\right) +
  2 \mu_1 \mu_2 \left|\bm{v}_1 \cdot \bm{v}_2\right| +
  \mu_2^2 \left(\bm{v}_2 \cdot \bm{v}_2\right)}{\alpha^2 + \beta^2}}.
\end{equation}

As far as the author can tell,
a condition number for the intersection of two planar B\'{e}zier curves
has not been described in the Computer Aided Geometric Design (CAGD)
literature. In \cite[Chapter~25, Equation 25.11]{Higham2002}
a more generic condition number is defined for the root of a nonlinear
algebraic system that is similar to the definition above.

For an example, consider the line
\(b_1(s) = \left[ \begin{array}{c c} 2s & 2s \end{array}\right]^T\)
and improperly parameterized line
\(b_2(t) = \left[ \begin{array}{c c} 4t^2 & 2 - 4t^2
\end{array}\right]^T\) which intersect at \(\alpha = \beta = 1/2\).
At the intersection we have \(J^{-1} = \frac{1}{8}
\left[ \begin{array}{c c} 2 & 2 \\ -1 & 1 \end{array}\right]\),
so that \(\bm{v}_1 \cdot \bm{v}_1 = \bm{v}_2 \cdot \bm{v}_2 =
5/64\) and \(\bm{v}_1 \cdot \bm{v}_2 = 3/64\). Since the
\(x\)-component of \(F(s, t)\) can be written as
\(2s - 4t^2 = 2 B_{1, 1}(s) - 4 B_{2, 2}(t)\) and the
\(y\)-component as \(2s + 4t^2 - 2 = 2 B_{1, 1}(s) - 2 B_{0, 2}(t)
- 2 B_{1, 2}(t) + 2 B_{2, 2}(t)\) we have
\begin{alignat}{2}
\mu_1 &= 2 B_{1, 1}(\alpha) &&+ 4 B_{2, 2}(\beta) = 2 \\
\mu_2 &= 2 B_{1, 1}(\alpha) + 2 B_{0, 2}(\beta) +
  2 B_{1, 2}(\beta) &&+ 2 B_{2, 2}(\beta) = 3.
\end{alignat}
Following~\eqref{eq:intersect-cond-num-too}, this gives
\(\kappa_{\alpha, \beta} = \sqrt{202}/8 \approx 1.78\).

>>>>

\usepackage{amsthm,amssymb,amsmath}
%% https://tex.stackexchange.com/a/396829/32270
\allowdisplaybreaks
\usepackage{bm}
%% H/T: https://tex.stackexchange.com/a/28334/32270
\usepackage{chngcntr}
\counterwithin{equation}{section}
%% H/T: https://tex.stackexchange.com/a/71153/32270
\usepackage[nottoc,notlot,notlof]{tocbibind}

\theoremstyle{definition}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{definition}{Definition}[section]

@@

\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{A 2-Norm Condition Number for B\'{e}zier Curve Intersection}
\rhead{Danny Hermes}

@@

\begin{abstract}
\noindent We present a short note describing a condition number
of the intersection of two B\'{e}zier curves.
\\ \\
\noindent \emph{Keywords}: B\'{e}zier curve, Curve intersection,
Condition number, Numerical analysis
\end{abstract}

@@

The problem of intersecting two planar B\'{e}zier curves is an important
one in Computer Aided Geometric Design (CAGD).
Many intersection algorithms have been described in the literature, both
geometric (\cite{Sederberg1986, Sederberg1990, Kim1998}) and algebraic
(\cite{Manocha:CSD-92-698}). Though the general convergence properties
of these algorithms have been studied (e.g. \cite{Schulz2009}),
no condition number for the intersection problem has been described in
the CAGD literature\footnote{As far as the author has been able to tell.
In many CAGD textbooks, there is a long review of methods for intersecting
two planar B\'{e}zier curves (e.g. \cite{Farin2001, SederbergNotes}) but no
mention of conditioning.}.

There are more generic condition numbers for rational polynomial systems
(\cite{Herman2015}) or nonlinear algebraic systems
(\cite[Chapter~25, Section 25.4]{Higham2002}). However, the condition
numbers with an algebraic focus (rather than an analytic one) often
require too much computation to be useful. The numerical analytic condition
numbers are in some ways too general to be useful for planar B\'{e}zier
curve intersection.

In this paper, we describe a simple relative root condition number for this
intersection problem. Since tangent intersections are to transversal
intersections as multiple roots are to simple roots of a function, this
condition number is infinite for non-transversal intersections.
We present a few examples verifying that the condition number increases as
a family of intersections approach an ill-behaved intersection.

\section{Preliminaries}

Throughout, we'll refer to a \emph{B\'{e}zier curve} as a parametric
plane curve given by
\begin{equation}
b(s) = \sum_{j = 0}^n \bm{b}_j B_{j, n}(s)
\end{equation}
where \(B_{j, n}(s) = \binom{n}{j} (1 - s)^{n - j} s^j\) is a Bernstein
polynomial.
When the parameter \(s \in \left[0, 1\right]\), the coefficients
\(B_{j, n}(s) \in \left[0, 1\right]\) as well and the evaluation is a convex
combination of the set of \emph{control points} \(\bm{b}_j \in \reals^2\).

A B\'{e}zier curve intersection is a root \(\left[\begin{array}{c}
\alpha \\ \beta \end{array}\right]\) of the function
\begin{equation}
F(s, t) = b_0(s) - b_1(t)
\end{equation}
where \(b_0(s)\) and \(b_1(t)\) are B\'{e}zier curves. Note that
\(F: \reals^2 \longrightarrow \reals^2\).

Each component \(x(s)\) and \(y(s)\) of a B\'{e}zier curve is a
polynomial in Bernstein form. For such a polynomial
\begin{equation}
p(s) = \sum_{j = 0}^n p_j B_{j, n}(s)
\end{equation}
the (absolute) condition number of evaluation is
\(\widetilde{p}(s) = \sum_{j = 0}^n \left|p_j\right| B_{j, n}(s)\)
(\cite{Farouki1987}) when the parameter \(s\) is in the unit interval.

\section{Conditioning of Generic Root-finding}

Consider a smooth function \(F: \reals^n \longrightarrow \reals^n\)
with Jacobian \(F_{\bm{x}} = J\). We want to consider a special class of
functions of the form \(F\left(\bm{x}\right) = \sum_j c_j
\phi_j\left(\bm{x}\right)\) where the basis
functions \(\phi_j\) are also smooth functions on \(\reals^n\)
and each \(c_j \in \reals\). We want to consider the effects on a root
\(\bm{\alpha} \in \reals^n\) of a perturbation in one of the
coefficients \(c_j\). We examine the perturbed function
\begin{equation}
G(x, \delta) = F\left(\bm{x}\right) + \delta \phi_j\left(\bm{x}\right).
\end{equation}
Since \(G\left(\bm{\alpha}, 0\right) = \bm{0}\), if \(J^{-1}\) exists at
\(\bm{x} = \bm{\alpha}\) then
the implicit function theorem tells us that we can define
\(\bm{x}\) via
\begin{equation}
G\left(\bm{x}\left(\delta\right), \delta\right) = \bm{0}.
\end{equation}
Taking the derivative with respect to \(\delta\) we find that
\(\bm{0} = G_{\bm{x}} \bm{x}_{\delta} + G_{\delta}\). Plugging in
\(\delta = 0\) we find that \(0 = J\left(\bm{\alpha}\right) \bm{x}_{\delta} +
\phi_j\left(\bm{\alpha}\right)\), hence we
conclude that
\begin{equation}
\bm{x}\left(\delta\right) = \bm{\alpha} - J\left(\bm{\alpha}\right)^{-1}
  \phi_j\left(\bm{\alpha}\right) \delta + \bigO{\delta^2}.
\end{equation}
This gives
\begin{equation}
\frac{\left \lVert J\left(\bm{\alpha}\right)^{-1}
  \phi_j\left(\bm{\alpha}\right) \right \rVert}{
  \left \lVert \bm{\alpha} \right \rVert}.
\end{equation}
as the relative condition number for a perturbation in \(c_j\).
By considering perturbations in \emph{all} of the coefficients:
\(\left|\delta_j\right| \leq \eps \left|c_j\right|\), a similar analysis
gives a root function
\begin{equation}
\bm{x}\left(\delta_0, \ldots, \delta_n\right) = \bm{\alpha} -
  J\left(\bm{\alpha}\right)^{-1} \sum_{j = 0}^n \delta_j
  \phi_j\left(\bm{\alpha}\right) + \bigO{\eps^2}.
\end{equation}
With this, we can define a root condition number

\begin{definition}\label{defn:abstract-cond-num}
For a smooth function \(F\left(\bm{x}\right) = \sum_j c_j
\phi_j\left(\bm{x}\right)\) parameterized by the coefficients
\(\left\{c_j\right\}\) with root \(\bm{\alpha}\) and Jacobian
\(J\left(\bm{\alpha}\right)\), we define a relative root condition
number
\begin{equation}
\kappa_{\bm{\alpha}} =
  \limsup_{\eps \to 0} \frac{\left \lVert\delta \bm{\alpha}
  \right \rVert / \eps}{\left \lVert\bm{\alpha}\right \rVert} =
  \lim_{\eps \to 0} \left(\sup_{\left|\delta_j\right| \leq
  \eps \left|c_j\right|} \frac{\left \lVert
  J\left(\bm{\alpha}\right)^{-1} \sum_j \delta_j
  \phi_j\left(\bm{\alpha}\right) \right \rVert / \eps}{
  \left \lVert\bm{\alpha}\right \rVert}\right).
\end{equation}
\end{definition}

In \cite[Chapter~25, Section 25.4]{Higham2002} a similar definition is
given. Instead of bounding the perturbations component-wise, it bounds
the entire perturbation vector
\begin{equation}
  \lim_{\eps \to 0} \left(\sup_{\left \lVert \bm{\delta} \right \rVert \leq
  \eps \left \lVert \bm{c} \right \rVert} \frac{\left \lVert
  J\left(\bm{\alpha}\right)^{-1} \sum_j \delta_j
  \phi_j\left(\bm{\alpha}\right) \right \rVert / \eps}{
  \left \lVert \bm{\alpha} \right \rVert}\right) =
  \left \lVert J^{-1} F_{\bm{c}} \right \rVert \frac{\left \lVert \bm{c}
  \right \rVert}{\left \lVert \bm{\alpha} \right \rVert}.
\end{equation}
While this has the benefit of having a closed form that is straightforward
to compute, it may be less useful than the condition number given in
Definition~\ref{defn:abstract-cond-num} since the larger coefficients
can dominate the rest.

\subsection{One-dimensional Case}

When \(n = 1\), due to the triangle inequality:
\begin{equation}\label{eq:tri-ineq}
\left|\delta \alpha\right| = \left|J^{-1} \sum_{j = 0}^n
  \delta_j \phi_j(\alpha)\right| \leq \frac{1}{\left|F'(\alpha)\right|}
  \sum_{j = 0}^n \left|\delta_j \phi_j(\alpha)\right|.
\end{equation}
The sign and magnitude of each \(\delta_j\) can be chosen to make
\(\delta_j \phi_j(\alpha) = \left|c_j \phi_j(\alpha)\right| \eps\),
hence for these values equality holds in the triangle inequality:
\begin{equation}
\left|\sum_{j = 0}^n \delta_j \phi_j(\alpha)\right| =
\eps \sum_{j = 0}^n \left|c_j \phi_j(\alpha)\right|.
\end{equation}
Thus we get a root condition number for a polynomial given in Bernstein form
\begin{equation}
\kappa_{\alpha} =
  \frac{1}{\left|\alpha F'(\alpha)\right|} \sum_{j = 0}^n \left|
  c_j \phi_j(\alpha)\right|.
\end{equation}
that agrees with the common definition (\cite{Farouki1987}) when the
\(\phi_j\) are specialized to Bernstein basis functions.

\section{Conditioning of B\'{e}zier Curve Intersection}

To define a condition number for the intersection of two planar B\'{e}zier
curves, we write the difference as
\begin{equation}
F(s, t) = \left[ \begin{array}{c} x_0(s) \\ 0 \end{array}\right] +
  \left[ \begin{array}{c} 0 \\ y_0(s) \end{array}\right] -
  \left[ \begin{array}{c} x_1(t) \\ 0 \end{array}\right] -
  \left[ \begin{array}{c} 0 \\ y_1(t) \end{array}\right].
\end{equation}
We can show that there is a closed form for the condition number given
by Definition~\ref{defn:abstract-cond-num}, specialized to the
2-norm.

\begin{theorem}
Let \(\left[\begin{array}{c} \alpha \\ \beta
\end{array}\right]\) be a transversal intersection of two planar
B\'{e}zier curves \(b_0(s)\) and \(b_1(t)\). Define the vectors
\begin{equation}
\widetilde{F}_{+} = \left[ \begin{array}{c}
  \widetilde{x}_0(\alpha) + \widetilde{x}_1(\beta) \\
  \widetilde{y}_0(\alpha) + \widetilde{y}_1(\beta) \end{array}\right] \quad
\text{and} \quad
\widetilde{F}_{-} = \left[ \begin{array}{c}
  \widetilde{x}_0(\alpha) + \widetilde{x}_1(\beta) \\
  -\widetilde{y}_0(\alpha) - \widetilde{y}_1(\beta)\end{array}\right].
\end{equation}
Then the root condition number of the intersection is the
greater of two vector norms:
\begin{equation}
\kappa_{\alpha, \beta} = \frac{1}{\sqrt{\alpha^2 + \beta^2}} \max \left\{
\left \lVert J\left(\alpha, \beta\right)^{-1} \widetilde{F}_{+}\right \rVert_2,
\left \lVert J\left(\alpha, \beta\right)^{-1} \widetilde{F}_{-}\right \rVert_2
\right\}.
\end{equation}
\end{theorem}

\begin{proof}
Let the curve \(b_0(s)\) be degree \(m\) and \(b_1(t)\) be degree \(n\).
Then \(F(s, t)\) can be written as \(2(m + 1) + 2(n + 1)\) terms:
\begin{equation}
F(s, t) =
  \sum_{i = 0}^m c_i^{(1)} \left[ \begin{array}{c}
  B_{i, m}(s) \\ 0 \end{array}\right] +
  \sum_{i = 0}^m c_i^{(2)} \left[ \begin{array}{c}
  0 \\ B_{i, m}(s) \end{array}\right] +
  \sum_{j = 0}^n c_j^{(3)} \left[ \begin{array}{c}
  -B_{j, n}(t) \\ 0 \end{array}\right] +
  \sum_{j = 0}^n c_j^{(4)} \left[ \begin{array}{c}
  0 \\ -B_{j, n}(t) \end{array}\right].
\end{equation}
Since \(F(s, t) = b_0(s) - b_1(t)\) we have Jacobian \(J(s, t) =
\left[ \begin{array}{c c} b_0'(s) & -b_1'(t) \end{array}\right]\). Since
a transversal intersection, we have
\(\det J(\alpha, \beta) \neq 0\). In a perturbation, we replace each
\(c_j^{(k)}\) with a \(\delta_j^{(k)}\) bounded by
\(\left|\delta_j^{(k)}\right| \leq \eps \left|c_j^{(k)}\right|\).
Writing \(J^{-1} = \left[ \begin{array}{c c}
\bm{v} & \bm{w} \end{array}\right]\), we have
\begin{multline}
J\left(\bm{\alpha}\right)^{-1} \sum_j \delta_j
  \phi_j\left(\bm{\alpha}\right) =
  \left[\sum_{i = 0}^m \delta_i^{(1)} B_{i, m}(\alpha) +
  \sum_{j = 0}^n \delta_j^{(3)} B_{j, n}(\beta)\right] \bm{v} \\
  + \left[\sum_{i = 0}^m \delta_i^{(2)} B_{i, m}(\alpha) +
  \sum_{j = 0}^n \delta_j^{(4)} B_{j, n}(\beta)\right] \bm{w} =
  \nu_1 \bm{v} + \nu_2 \bm{w}
\end{multline}
where
\begin{align}
\left|\nu_1\right| / \eps &\leq \sum_{i = 0}^m
  \left|c_{i}^{(1)}\right| B_{i, m}\left(\alpha\right) + \sum_{j = 0}^n
  \left|c_{j}^{(3)}\right| B_{j, n}\left(\beta\right) =
  \widetilde{x}_0(\alpha) + \widetilde{x}_1(\beta) = \mu_1 \\
\left|\nu_2\right| / \eps &\leq \sum_{i = 0}^m
  \left|c_{i}^{(2)}\right| B_{i, m}\left(\alpha\right) + \sum_{j = 0}^n
  \left|c_{j}^{(4)}\right| B_{j, n}\left(\beta\right) =
  \widetilde{y}_0(\alpha) + \widetilde{y}_1(\beta) = \mu_2.
\end{align}
As in \eqref{eq:tri-ineq}, the bound can be attained by choosing the
sign and magnitude of each perturbation so that
\(\delta_j^{(k)} B_{j, d} = \eps \left|c_j^{(k)}\right| B_{j, d}\).
The factor of \(\eps\) can be cancelled to give condition number
\begin{align}
\kappa_{\alpha, \beta} &= \frac{1}{\sqrt{\alpha^2 + \beta^2}}
  \sup_{\left|\nu_k\right| \leq \mu_k} \left \lVert \nu_1 \bm{v} +
  \nu_2 \bm{w} \right \rVert_2 \\
  &=
  \sqrt{\frac{\sup_{\left|\nu_k\right| \leq \mu_k}
  \nu_1^2 \left(\bm{v} \cdot \bm{v}\right) +
  2 \nu_1 \nu_2 \left(\bm{v} \cdot \bm{w}\right) +
  \nu_2^2 \left(\bm{w} \cdot \bm{w}\right)}{\alpha^2 + \beta^2}}
  \label{eq:intersect-cond-num}.
\end{align}
Now we seek to maximize the objective function \(\theta(\nu_1, \nu_2) =
\nu_1^2 \left(\bm{v} \cdot \bm{v}\right) +
2 \nu_1 \nu_2 \left(\bm{v} \cdot \bm{w}\right) +
\nu_2^2 \left(\bm{w} \cdot \bm{w}\right)\) in the rectangle
\(\left[-\mu_1, \mu_1\right] \times \left[-\mu_2, \mu_2\right]\).

To find interior critical points, we solve the system \(\theta_{\nu_1} =
\theta_{\nu_2} = 0\):
\begin{equation}
\left[ \begin{array}{c c}
  2 \bm{v} \cdot \bm{v} & 2 \bm{v} \cdot \bm{w} \\
  2 \bm{v} \cdot \bm{w} & 2 \bm{w} \cdot \bm{w} \end{array}\right]
\left[ \begin{array}{c} \nu_1 \\ \nu_2 \end{array}\right] =
\left[ \begin{array}{c} 0 \\ 0 \end{array}\right].
\end{equation}
This system has the unique solution \(\nu_1 = \nu_2 = 0\) unless
\(\|\bm{v}\|_2 \|\bm{w}\|_2 = \left|\bm{v} \cdot \bm{w}\right|\).
By the Cauchy-Schwarz inequality, this can only occur if \(\bm{v}\) and
\(\bm{w}\) are parallel; since \(J^{-1}\) is invertible, we know they
are not. Hence \(\theta(0, 0) = 0\) is the only interior critical point and
it is the global minimum.

Along the boundary of the rectangle,
we fix one of \(\nu_1\) or \(\nu_2\) and the resulting univariate function is
an up-opening parabola. For example, fixing \(\nu_2 = c\) gives
\(\theta(\nu_1, c) =
\nu_1^2 \left(\bm{v} \cdot \bm{v}\right) +
\nu_1\left[2 c \left(\bm{v} \cdot \bm{w}\right)\right] +
c^2 \left(\bm{w} \cdot \bm{w}\right)\) which has positive lead coefficient
\(\|\bm{v}\|_2^2\). The lead coefficient cannot be \(0\) since if \(\bm{v}\)
were the zero vector we'd have \(\det J = 0\).
Since \(\theta\) is an up-opening parabola along the boundary, any critical
point must be a local minimum.

Thus we know the maximum occurs at two of the four corners of the
rectangle. Due to sign cancellation, this leads to one of two values
\(\theta =
\mu_1^2 \left(\bm{v} \cdot \bm{v}\right) \pm
2 \mu_1 \mu_2 \left(\bm{v} \cdot \bm{w}\right) +
\mu_2^2 \left(\bm{w} \cdot \bm{w}\right)\), the largest of which is
\(\mu_1^2 \left(\bm{v} \cdot \bm{v}\right) +
2 \mu_1 \mu_2 \left|\bm{v} \cdot \bm{w}\right| +
\mu_2^2 \left(\bm{w} \cdot \bm{w}\right)\). Thus
\begin{equation}\label{eq:intersect-cond-num-too}
\kappa_{\alpha, \beta} = \sqrt{\frac{\mu_1^2
  \left(\bm{v} \cdot \bm{v}\right) +
  2 \mu_1 \mu_2 \left|\bm{v} \cdot \bm{w}\right| +
  \mu_2^2 \left(\bm{w} \cdot \bm{w}\right)}{\alpha^2 + \beta^2}}.
\end{equation}
Note that \(\widetilde{F}_{\pm} = \left[ \begin{array}{c} \mu_1 \\ \pm \mu_2
\end{array}\right]\), so
\begin{equation}
\left \lVert J\left(\alpha, \beta\right)^{-1} \widetilde{F}_{\pm}
  \right \rVert_2 = \left \lVert \left[ \begin{array}{c c} \bm{v} & \bm{w}
  \end{array}\right] \widetilde{F}_{\pm} \right \rVert_2 =
  \sqrt{\mu_1^2 \left(\bm{v} \cdot \bm{v}\right) \pm
  2 \mu_1 \mu_2 \left(\bm{v} \cdot \bm{w}\right) +
  \mu_2^2 \left(\bm{w} \cdot \bm{w}\right)}
\end{equation}
gives each of the two values that produce the maximum value.
\end{proof}

\subsection{Transversal Intersection}
